---
title: "notebook20181101"
author: "Mark Hagemann"
date: "November 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


It's time to package up these Q estimates and send them along!

This means associating actual times and river locations with the "reach sets" I'm inverting. 

I don't have the actual estimates on my laptop here, but I can work from an upstream object. 

- Use bds_reach and bds_reach_mean (probably just the latter). 
    - No time info, just space indices and DAWG matrices.
- reachcases2_mean has the info. 
    - This maps directly to bds_reach_mean (see munge/07-bamprep.R)

```{r}
fromcache("bds_reach_mean")
fromcache("reachcases2_mean")

#' A function to collapse a matrix along a dimension. 
clps <- function(x, dim, clpsfun = unique, ...) {
  unq <- apply(x, dim, clpsfun, ...)
  out <- unlist(lapply(unq, na.omit))
  if (length(out) > dim(x)[dim]) {
    browser()
    stop("more than one nonmissing value present along dim")
  }
  out
}

bds_times <- map(reachcases2_mean, ~as.Date(clps(.$date, 2)))
bds_locs <- map(reachcases2_mean, ~clps(.$x, 1, clpsfun = median, na.rm = TRUE))


```

Now make a data.frame to join by location (index) and time index.

tidyr has stuff for this, right?

```{r}

tojoin0 <- map2(bds_times, bds_locs, 
                function(x, y) data.frame(time = rep(x, length(y)),
                                timeind = rep(1:length(x), length(y)),
                                loc = rep(y, each = length(x)),
                                locind = rep(1:length(y), each = length(x))))

tojoindf <- bind_rows(tojoin0, .id = "setid")
```

That should get me ready to join to the qests_reach object from invert.R.

