---
title: "notebook20181010"
author: "Mark Hagemann"
date: "October 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Picking up where I left off yesterday. 

- I've already recreated the swotlists
- Still need to make "cases"
- Then graphical summaries
    - What I mean about imputation--constant widths
    - negative slopes--flat reaches
    - same-latlon, different x_km


Make a raster of missing (including non-positive-slope) data

```{r}
dim(mscase$S)

msdf %>% glimpse() %>% 
  ggplot(aes(x = time, y = loc, fill = is.na(S))) + 
  geom_raster()
ggsave("../graphs/badslope.png", width = 8, height = 6, units = "in", dpi = 200)
```

That's a really funky plot. How to interpret? How about a regular slope plot? 

```{r}
fromcache("joindf")
sdf <- joindf[c("timeind", "loc", "S", "dx")]
sdf <- sdf[sdf$dx == 1000]
rm(joindf); gc()
 
ggplot(sdf, aes(x = timeind, y = loc, fill = S)) + 
  geom_raster()
  
ggsave("../graphs/slopeplot.png", width = 8, height = 6, units = "in", dpi = 200)
```

```{r}
wdf <- joindf[c("timeind", "loc", "W")]
rm(joindf); gc()
 
ggplot(wdf, aes(x = timeind, y = loc, fill = log(W))) + 
  geom_raster()
  
ggsave("../graphs/widthplot.png", width = 8, height = 6, units = "in", dpi = 200)
```

Need to do some timeseries instead

```{r}
# fromcache("mscase")
randloc <- sample(1:(nrow(mscase$W - 1)), 1)
ntimes <- 8413 # Max is 8413.
randtstart <- sample(1:(ncol(mscase$W) - (ntimes + 1)), 1)
# 
# dev.new()
par("mfrow" = c(1, 2))
plot(mscase$W[randloc, randtstart + 0:ntimes], type = "l", xlab = "time", ylab = "width")
plot(mscase$H[randloc, randtstart + 0:ntimes], type = "l", xlab = "time", ylab = "height")
lines(mscase$H[randloc + 1, randtstart + 0:ntimes], col = "red")

```


Clearly these are interpolated. Flat interpolation for width; linear interpolation for height. I think this is problematic. (Why?)

- No way to know how far from the nearest measurement
- Slope is a finite difference. Possible (though no evidence so far) that an interpolated 
- Hydrologic variation takes place at finer resolution than temporal sampling present here. 
- dA calculation requires simultaneous width and height measurement. 
- Almost by definition, interpolated points can't add any information, and would overestimate the confidence of our estimates. 


