---
title: "notebook20181008"
author: "Mark Hagemann"
date: "October 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

How do I join locations in height and widht mississippi data?


```{r}
heightmat %>% str()
missmat %>% str()
```

```{r}
widthdf %>% str()
heightdf %>% str()
```

I need to make a plot showing where and when width and height data are (not) missing. This should be done on as raw as possible of data. 

First I need to ascertain location data for widths. Is `FD` really location?

```{r}
widthdf$FD %>% head()

widthdf %>% 
  sample_n(10000) %>% 
  ggplot(aes(x = X, y = Y, color = FD)) + 
  geom_point() + coord_quickmap()

heightdf %>% 
  sample_n(10000) %>% 
  ggplot(aes(x = lon, y = lat, color = x)) + 
  geom_point() + coord_quickmap()

```

It sure is! How does `widthdf$FD` match against `heightdf$x`? First I need to know whether I can join by lat and lon. 

It appears that I can convert FD --> x by converting to meters (Better vice versa).

```{r}
widthlocs <- sort(unique(widthdf$FD))
heightlocs <- sort(unique(heightdf$x / 1000))

head(widthlocs)
head(heightlocs)

hist(widthlocs)
hist(heightlocs)
```

Now an interactive map showing difference in locations. 

```{r}
wlocdf <- widthdf %>% 
  transmute(x_km = FD, lat = Y, lon = X) %>% 
  group_by(x_km, lat, lon) %>% 
  summarize(n = n())

hlocdf <- heightdf %>% 
  transmute(x_km = x / 1000, lat, lon) %>% 
  group_by(x_km, lat, lon) %>% 
  summarize(n = n())

locdf <- list(W = wlocdf, H = hlocdf) %>% 
  bind_rows(.id = "var")
```

```{r}
library(leaflet)

pal <- function(var) {
  out <- ifelse(var == "H", "red", "blue")
}
locdf %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~lon, lat = ~lat, color = ~pal(var), 
                   popup = ~sprintf("lat: %s<br/>lon: %s<br/>km:%s<br/>var:%s", 
                                    lat, lon, x_km, var))
```



## Updated data from Steve

```{r}
width0 <- readMat("../data/MississippidailywidthGrid.mat")
width1 <- width0$Wpackage %>% 
  setNames(attr(., "dimnames")[[1]])

curvenames <- dimnames(width1$Curves)[[1]]
curves <- setNames(as.data.frame(t(width1$Curves[, 1, ])), curvenames)

width2 <- melt(width1$w, na.rm = FALSE) %>% 
  mutate(lat = rep(as.vector(width1$lat), nrow(width1$w)),
         lon = rep(as.vector(width1$lon), nrow(width1$w)))

height1 <- width1$Hdexes %>% 
  setNames(attr(., "dimnames")[[1]])
str(height1, 1)
str(height1$Tsat, 1)

height2 <- melt(height1$H) %>% 
  mutate(time = rep(as.vector(height1$T), 
                    length(as.vector(height1$X))),
         lat = rep(as.vector(height1$lat), 
                   length(as.vector(height1$T))),
         lon = rep(as.vector(height1$lon), 
                   length(as.vector(height1$T))),
         X = rep(as.vector(height1$X), 
                 length(as.vector(height1$T))),
         W = rep(as.vector(height1$W), 
                 length(as.vector(height1$T))))
```

Now look at the locations. Judging by dimensions, it looks like the same dates are represented--just locations differ. 

```{r}
wlocs <- width2 %>% 
  group_by(lat, lon) %>% 
  summarize(n = n())

hlocs <- height2 %>% 
  select(lat, lon, X) %>% 
  group_by(lat, lon, X) %>% 
  summarize(n = n())

wlocs$X <- NA_real_
locdf <- list(W = wlocs, H = hlocs) %>% 
  bind_rows(.id = "var")


locdf %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~lon, lat = ~lat, color = ~ifelse(var == "W", "red", "blue"),
                   popup = ~sprintf("lat: %s<br/>lon: %s<br/>km:%s<br/>var:%s", 
                                    lat, lon, X, var))

# No height data downstream of a certain point near the mouth. Omit these:
# lat < 30, lon > -90.28

height3 <- height2 %>% 
  filter(!(lat < 30 & lon > -90.28))
```

Now select the in-common locations. 

```{r}
wlocs2 <- wlocs %>% 
  ungroup() %>% 
  mutate(lat = round(lat, digits = 4), lon = round(lon, digits = 4),
         locstr = paste(lat, lon, sep = ";")) %>% 
  select(-X)
hlocs2 <- hlocs %>%
  ungroup() %>% 
  mutate(lat = round(lat, digits = 4), lon = round(lon, digits = 4),
         locstr = paste(lat, lon, sep = ";"))

commonlocs <- inner_join(wlocs2, hlocs2, by = c("lat", "lon", "locstr"))

wlocs2 %>% 
  filter(!(locstr %in% commonlocs$locstr)) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~lon, lat = ~lat)
```

Filter data to only these locations.

```{r}
width3 <- width2 %>% 
  mutate(locstr = paste(round(lat, digits = 4), lon = round(lon, digits = 4),
                        sep = ";")) %>% 
  filter(locstr %in% commonlocs$locstr)

height3 <- height2 %>% 
  mutate(locstr = paste(round(lat, digits = 4), lon = round(lon, digits = 4),
                        sep = ";")) %>% 
  filter(locstr %in% commonlocs$locstr)
  
```

Some locations still don't overlap perfectly, but I can roll with that. 

Somehow this isn't resulting in W, H datasets with the same dimensions, even though subsetting to in-common locations should--same times are represented in original data structures. I'll need to loop back and subset before I melt.

```{r}
wlocs_orig <- paste(round(width1$lat, digits = 4), round(width1$lon, digits = 4), sep = ";")
keepinds_w <- wlocs_orig %in% commonlocs$locstr

hlocs_orig <- paste(round(height1$lat, digits = 4), round(height1$lon, digits = 4), sep = ";")
keepinds_h <- hlocs_orig %in% commonlocs$locstr
```

Now use that to subset and retransform.

```{r}
str(width4, 1)
width4 <- within(width1, {
  w = w[, keepinds_w]
  lat = lat[1, keepinds_w]
  lon = lon[1, keepinds_w]
})
height4 <- within(height1, {
  H = H[, keepinds_h]
  lat = lat[1, keepinds_h]
  lon = lon[1, keepinds_h]
  X = X[1, keepinds_h]
})


width5 <- melt(width4$w, na.rm = FALSE) %>% 
  mutate(lat = rep(as.vector(width4$lat), nrow(width4$w)),
         lon = rep(as.vector(width4$lon), nrow(width4$w)))

height5 <- melt(height4$H, na.rm = FALSE) %>% 
  mutate(time = rep(as.vector(height4$T), 
                    length(as.vector(height4$X))),
         lat = rep(as.vector(height4$lat), 
                   length(as.vector(height4$T))),
         lon = rep(as.vector(height4$lon), 
                   length(as.vector(height4$T))),
         X = rep(as.vector(height4$X), 
                 length(as.vector(height4$T))))
```

Latest snag: a bunch of heights have the same lat/lon, but different X.  



```{r}
commonlocs[c(2000:2030, 2080:2110, 2160:2190, 2200:2230), ] %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(popup = ~paste(X))
    
```

Sho 'nuff. Two choices: 1. omit these locations; 2. trust the X. Also possible these are problematic lake locations, so in that case I should omit. 

```{r}
commonlocs2 <- commonlocs %>% 
  group_by(lat, lon, locstr) %>% 
  summarize(n = n(), X = X[1]) %>% 
  ungroup() %>% 
  filter(n == 1) %>% 
  select(-n)

wlocs_orig2 <- paste(round(width1$lat, digits = 4), round(width1$lon, digits = 4), sep = ";")
keepinds_w2 <- wlocs_orig2 %in% commonlocs2$locstr

hlocs_orig2 <- paste(round(height1$lat, digits = 4), round(height1$lon, digits = 4), sep = ";")
keepinds_h2 <- hlocs_orig2 %in% commonlocs2$locstr
```

One more go at this. 

```{r}

width6 <- within(width1, {
  w = w[, keepinds_w2]
  lat = lat[1, keepinds_w2]
  lon = lon[1, keepinds_w2]
})
height6 <- within(height1, {
  H = H[, keepinds_h2]
  lat = lat[1, keepinds_h2]
  lon = lon[1, keepinds_h2]
  X = X[1, keepinds_h2]
})


width7 <- melt(width6$w, na.rm = FALSE) %>% 
  mutate(lat = rep(as.vector(width6$lat), nrow(width6$w)),
         lon = rep(as.vector(width6$lon), nrow(width6$w)))

height7 <- melt(height6$H, na.rm = FALSE) %>% 
  mutate(time = rep(as.vector(height6$T), 
                    length(as.vector(height6$X))),
         lat = rep(as.vector(height6$lat), 
                   length(as.vector(height6$T))),
         lon = rep(as.vector(height6$lon), 
                   length(as.vector(height6$T))),
         X = rep(as.vector(height6$X), 
                 length(as.vector(height6$T))))

glimpse(width7)
```

BOOYAH! Now clean it up for a munge script. Main points are (working backward):

- width7 <--transform-- width6 <--subset-- width1 + keepinds_w2
    - width1 <--subset,-set-names-- width0 <--(read in)
    - keepinds_w2 <--contained-in-- wlocs_orig2 + commonlocs2$locstr
        - wlocs_orig2 <--paste-columns-- width1
        - commonlocs2 <--filter-lakes-- commonlocs <--inner-join-- wlocs2 + hlocs2
            - wlocs2 <--round-latlon-- wlocs <--unique-locs-- width2 <--tabulate-- width1
            - hlocs2 <--round-latlon-- hlocs <--unique-locs-- height2 <--tabulate-- height1 <--subset-- width1
- height7 <--transform-- height6 <--subset-- height1 + keepinds_h2
    - height1 <--subset,-set-names-- width1
    - keepinds_h2 <--contained-in--hlocs_orig2 + commonlocs2$locstr
        - hlocs_orig2 <-- paste-columns-- height1


OK, now it's in a script. Next make that fig I've had in mind for a while now:

```{r}
obsdf %>% 
  filter(timeind == 1) %>% 
  ggplot(aes(x = x_km, y = H)) + 
  geom_line()
```

