---
title: "data summary"
author: "Mark Hagemann"
date: "October 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Raw data and structure
The raw data come from two files--one for width, "Mississippi_Widthgrid3.mat", and one for heights, "TERPMississippi.mat".

```{r}
# missmat <- readMat("data/Mississippi_Widthgrid3.mat")
str(missmat$Wgrid, 1)

# heightmat <- readMat("data/TERPMississippi.mat")
str(heightmat, 1)
```


Within `Mississippi_widthgrid3.mat`, the width data are in the `Wgrid` struct, containing

- `Wgrid`, a 1649 x 2740 matrix of with data
- `T`, a 1649 x 1 column vector of times, given as days since the date "0000-01-01"
- `FD`, a 1 x 2740 row vector of locations, in km from some unknown start point (downstream).
- `X`, a row vector giving location longitude
- `Y`, a row vector giving location latitude

Witin `TERPMississippi.mat`, the data are given as

- `TERP`, a 8414 x 2723 matrix of height data
- `x`, a row vector of along-river distance in meters
- `y`, a vector of dates dates (days since "0000-01-01")
- `s`, a scalar denoting ???
- `lat`, a row vector of latitudes
- `lon`, a row vector of longitudes

```{r}
widthdf$FD %>% summary()

heightmat$x %>% as.vector() %>% str()
str(heightmat, 1)

str(heightmat$x)
str(widthdf)
str(missmat)
attr(missmat, "dimnames")
attributes(missmat[[1]])
```



These I transform and join together into a km-scale (node-scale?) data.frame (tabular data structure) with columns

- `date`
- `x`, along-river distance (identical to TERPMississippi `x`)
- `H`, height
- `W`, width
- `dH`, first-order finite-difference (in space) for `H`
- `dx`, first-order finite-difference (in space) for `x`
- `S`, slope = `dH / dx`



























